The Soulgem Paper

### 2011-09-24 expectationPeopleTable.tex
space savers included in the table
Second draft of expectations table. Now with a respectable caption :-P.

\def\w{\rrr{0}{1}{1}{\color{white}}}
\def\l{\rrr{0}{1}{1}{\color{mygray}}}
\def\g{\rrr{0}{1}{1}{\color{yourgray}}}
\def\b{\rrr{0}{1}{1}{\color{black}}}
\def\0{\w}
\def\1{\l}
\def\2{\b}
\def\angle{90}

\begin{table*}[tb]

@@

&\multicolumn{2}{c}{\begin{rotate}{\angle}SW Directors\end{rotate} }
&\multicolumn{2}{c}{\begin{rotate}{\angle}Tech Leads\end{rotate} }
&\multicolumn{2}{c}{\begin{rotate}{\angle}Team Leads\end{rotate} }
&\multicolumn{2}{c}{\begin{rotate}{\angle}Developers\end{rotate} }
&\multicolumn{2}{c}{\begin{rotate}{\angle}Qa \& Ops\end{rotate} }
&\multicolumn{2}{c}{\begin{rotate}{\angle}Prod Mgmt\end{rotate} }
&\multicolumn{2}{c}{\begin{rotate}{\angle}Project Mgmt\end{rotate}} 
&\multicolumn{2}{c}{\begin{rotate}{\angle}Support \& Field\end{rotate}} \\

@@

& Groups 
& A & B
& A & B
& A & B
& A & B 
& A & B
& A & B
& A & B
& A & B\\
\bottomrule

@@

>>>>

\def\w{\rrr{0}{1}{1}{\color{white}}}
\def\l{\rrr{0}{1}{1}{\color{mygray}}}
\def\g{\rrr{0}{1}{1}{\color{yourgray}}}
\def\b{\rrr{0}{1}{1}{\color{black}}}
\def\0{\w}
\def\1{\l}
\def\2{\b}
\def\angle{60}

\begin{table*}[tb!]

@@

&\multicolumn{2}{l}{\begin{rotate}{\angle}SW Directors\end{rotate} }
&\multicolumn{2}{l}{\begin{rotate}{\angle}Tech Leads\end{rotate} }
&\multicolumn{2}{l}{\begin{rotate}{\angle}Team Leads\end{rotate} }
&\multicolumn{2}{l}{\begin{rotate}{\angle}Developers\end{rotate} }
&\multicolumn{2}{l}{\begin{rotate}{\angle}QA \& Ops\end{rotate} }
&\multicolumn{2}{l}{\begin{rotate}{\angle}Product Mgmt\end{rotate} }
&\multicolumn{2}{l}{\begin{rotate}{\angle}Project Mgmt\end{rotate}} 
&\multicolumn{2}{l}{\begin{rotate}{\angle}Support \& Field\end{rotate}} \\

@@

& Organizations 
& G & C
& G & C
& G & C
& G & C 
& G & C
& G & C
& G & C
& G & C\\
\multicolumn{18}{c}{\2: Highly Expected \1: Somewhat Expected \0: Not Expected}\\

@@

\caption{Assignment of expectations to people in our field sites. This matrix only includes our interviewees in both organizations; about half of the total number of organization members. Interviewees are clustered approximately by labels, despite label variations. Within each label cluster there is a further subdivision by organization (``G'' stands for Gallium, ``C'' for Cobalt). The colouring of each cell is necessarily subjective, but it corresponds to a rough consensus view of the expectations placed on each individual.}
